\normalfont{A statistical analysis on factors that contributed/slowed down the spread of COVID-19}

### 2020-09-07 Manuscript/Manuscript.tex
pub

>>>>

Looking to the Fig. \ref{Regions_CorrMatrix},\ref{Regioni_PCA_loadings} and \ref{Regions_FULL_PCA} we found a positive correlation between the Mean Income and the Cases, as for the provinces,. This relation has the same explanation that was found in the previous paragraph. Furthermore here, since the overall number of tests are available as well as the number of deaths for COVID19, we see that these two normalized quantities are positively correlated with the cases. The causal connection for these three quantities is simple: in order to validate that a patient is infected a test is required, and a part of the infected patient are going to die for COVID19. The correlation matrix also highlights that there is a positive correlation between the number of people for general practitioner and the number of cases; moreover a higher number of normalized visit is negatively correlated with the number of cases and the mortality. The causal reason for this statistical correlation is currently under discussion but an interesting perspective, at a journalistic level, was performed on a Italian newspaper \cite{24plus}: the idea of the author is that the general practitioners play the role of sensor/sentinel for the COVID19 cases; as long as their number and their presence in all the cities is reduced, the health service is less sensitive to find new cases and the diffusion of the virus is favoured.  On the other side the quality index LEA,the normalized number of medical and the number of Public Structure Normalized  guards seems to play a weaker role. Finally it is worth nothing that, as shown in Fig. \ref{Region_variances} in the 2D plots \ref{Regioni_PCA_loadings} and \ref{Regions_FULL_PCA} only the 26.7 $ \% $ of information is lost.
